Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-30 main.Rmd
panel.border changed for cricket example

# filter(fielding_wckts %in% c(0,1)) %>%
#
 cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
# + geom_boxplot(width = 0.5, aes(colour = lag_field))
```

>>>>

# filter(fielding_wckts %in% c(0,1)) %>%
#
 cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +
        theme(axis.ticks = element_blank(), legend.background = element_blank(),
            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
```
